Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Explain Population, Frame and Sample of the Pollster
Explain Population, Frame and Sample of the Pollster

>>>>

The population for the poll includes adults aged 18 and over across all 50 states and the District of Columbia. The sampling frame was constructed through ABS, leveraging the US Postal Service's Computerized Delivery Sequence (CDS), a comprehensive, regularly updated list of residential addresses. The primary source for participants is the SSRS Opinion Panel, which includes both ABS and telephone survey data to capture hard-to-reach demographics, like non-Internet users. The survey ultimately included 1,005 adults, including registered and likely voters, with weighted samples to ensure proportional representation.
